Getting Started with the Graded Response Model (GRM): An introduction and tutorial in R

### 2025-01-14 manuscript.qmd
Adding link, vol, number to the bibtex entry in README

| Model                       | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
|-----------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
| 1-PL Model (Rasch Model)    | 1\. Estimates only item difficulties (*b*). 2. Assumes that all items have equal discrimination parameters (*a*). 3. Item and person parameters are independent.                                                                                             | Dichotomous | Correct/Incorrect (0/1) |
| 2-PL Model                  | 1\. Estimates item difficulties (*b*) and item discrimination (*a*). 2. Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.                                                                                         | Dichotomous | Correct/Incorrect (0/1) |
| 3-PL Model                  | 1\. Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*). 2. Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses. | Dichotomous | Correct/Incorrect (0/1) |
| Graded Response Model (GRM) | 1\. Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style). 2. Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.                                                       | Polytomous  | Ordered Categories      |

>>>>

| Model | Key Characteristics | Data Type | Response Options |
|----|----|----|----|
| 1-PL Model (Rasch Model) | 1\. Estimates only item difficulties (*b*). 2. Assumes that all items have equal discrimination parameters (*a*). 3. Item and person parameters are independent. | Dichotomous | Correct/Incorrect (0/1) |
| 2-PL Model | 1\. Estimates item difficulties (*b*) and item discrimination (*a*). 2. Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary. | Dichotomous | Correct/Incorrect (0/1) |
| 3-PL Model | 1\. Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*). 2. Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses. | Dichotomous | Correct/Incorrect (0/1) |
| Graded Response Model (GRM) | 1\. Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style). 2. Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item. | Polytomous | Ordered Categories |
